Equalizer Programming Guide

### 2007-12-10 Developer/ProgrammingGuide/paper.tex
Update Programming Guide after last change.
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.1.4 for Equalizer 0.4+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.0.1   & Nov 06, 2007 & Fixed Typo\\
    1.1     & Nov 12, 2007 & Adapted distributed objects\\
    1.1.1   & Nov 16, 2007 & Minor improvements based on lulu.com print\\
    1.1.2   & Nov 19, 2007 & Minor improvements based on feedback\\
    1.1.3   & Nov 23, 2007 & Add OpenGL extension handling\\
    1.1.4   & Nov 26, 2007 & Changes caused by removal of glX event thread\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

{\footnotesize\begin{lstlisting}
class NodeFactory : public eq::NodeFactory
{
public:
    virtual eq::Config*  createConfig()  { return new eqPly::Config; }
    virtual eq::Node*    createNode()    { return new eqPly::Node; }
    virtual eq::Pipe*    createPipe()    { return new eqPly::Pipe; }
    virtual eq::Window*  createWindow()  { return new eqPly::Window; }
    virtual eq::Channel* createChannel() { return new eqPly::Channel; }
};
\end{lstlisting}}

>>>>

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.1.5 for Equalizer 0.4+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.0.1   & Nov 06, 2007 & Fixed Typo\\
    1.1     & Nov 12, 2007 & Adapted distributed objects\\
    1.1.1   & Nov 16, 2007 & Minor improvements based on lulu.com print\\
    1.1.2   & Nov 19, 2007 & Minor improvements based on feedback\\
    1.1.3   & Nov 23, 2007 & Add OpenGL extension handling\\
    1.1.4   & Nov 26, 2007 & Changes caused by removal of glX event thread\\
    1.1.5   & Dec 10, 2007 & NodeFactory API changes\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

{\footnotesize\begin{lstlisting}
class NodeFactory : public eq::NodeFactory
{
public:
    virtual eq::Config*  createConfig()  
        { return new eqPly::Config; }
    virtual eq::Node*    createNode( eq::Config* parent )  
        { return new eqPly::Node( parent ); }
    virtual eq::Pipe*    createPipe( eq::Node* parent )
        { return new eqPly::Pipe( parent ); }
    virtual eq::Window*  createWindow( eq::Pipe* parent )
        { return new eqPly::Window( parent ); }
    virtual eq::Channel* createChannel( eq::Window* parent )
        { return new eqPly::Channel( parent ); }
};
\end{lstlisting}}
